Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Add new references and complete related work section

@@

@@

Then, we split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
follow the flow shown in figure \ref{fig-eg} and complete the whole application cycle, in the end producing a database 
of analysed tickets, as well as plots and statistics for investigating correlations, saved on the filesystem.

In the following two subsections we describe how we designed and implemented the commands mentioned above.

@@

We have interacted with the Jira Server REST API which has very good documentation written by the Atlassian team. After getting
familiar with all the features the REST API offers, we have opted for getting paginated issues from the server, which means 
slicing the whole set of tickets into multiple smaller arrays to improve performance and reduce the load on the server. We also
specified to Jira exactly what set of issue fields to return and, eventually, while responses were retrieved from the instance,
we began storing them into our Bolt DB instance. The way we chose to store them was to set the issue key (i.e. unique 
identifier that differentiates a ticket from all others across all projects inside a Jira instance) as the key of the pair and
the value is the whole representation of an issue (e.g. attachments, story points, priority) as a JSON encoded value. This
helped us reduce the size of the database once we reached hundreds of thousands of tickets.

@@

There are other fields that can be configured inside Jira, including custom fields, but we did not collect them as they would not 
have been helpful in conducting the analysis. However, in addition to the fields we saved, we also store grammar correctness scores 
(i.e. number of grammar mistakes identified in summary, description and comments), sentiment scores (i.e. sentiment drawn from summary 
and description), whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
Even though all of them, apart from grammar and sentiment scores, can be computed locally, we store them because of performance issues
due to the very large size of the database.

@@

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs;
\end{itemize}

>>>>

In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
questions in this paper (Section \ref{correlations}):

@@

The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
makes for a valuable bug report through qualitative analysis. 
After conducting interviews with over 450 developers, one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.

Strengthening the argument that readability matters considerably in bug report 
quality is the work of Hooimeijer et. al \cite{hooimeijer2007modeling}. They ran an analysis over
27000 bug reports from the Mozilla Firefox project, looking at self-reported 
severity, readability, daily load, submitter reputation and changes over time. 
After running the evaluation, they not only found out about the importance of
readability in bug reports, but also that attachment and comment counts are 
valuable for faster triaging and that patch count, for example, does not
contribute in the same manner as the previous two.

Another research that agrees that stack traces are helpful in solving bug
reports faster is the one performed by Schroter et. al \cite{schroter2010stack}. They conducted
the whole experiment on the Eclipse project. They first extracted the stack
traces using the infoZilla tool(\cite{bettenburg2008extracting}), followed by
linking the stack traces to changes in the source code (change logs) by mining
the version repository of the Eclipse project. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame, with 40\% being fixed in exactly the first
stack frame.

Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in \cite{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.

Bettenburg et. al \cite{bettenburg2012using} present in their work an application
called infoZilla. This tool can
parse bug reports and correctly extract stack traces, patches and source code. 
When evaluated on over 150,000 bug reports, it proved to have a very high rate of over 97\% accuracy.
We applied some of the techniques shown in the study and successfully managed to 
retrieve stack traces as well with a great accuracy.

One other type of information that could be extracted and used for valuable
purposes is the summary of a bug report, as shown in the work of 
Rastkar et. al \cite{rastkar2010summarizing}. The authors wanted to determine if bug reports
could be summarized effectively and automatically so that developers would
need only analyze summaries instead of full tickets. Firstly, they asked
university students to volunteer to annotate the bug reports collected from
various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
a summary of maximum 250 words in their own sentences. These human-produced 
annotations were then used by algorithms to learn how to effectively summarize a 
bug report.  Afterwards, the authors asked the end users of these bug reports, the 
software developers, to rate the summaries against the original bug reports.
They eventually learned that existing conversation-based extractive summary
generators trained on bug reports produce the best results.

We tried to apply the technique presented in the work of Fischer et. al \cite{fischer2003analyzing},
where they present a way to track specific version controlled branches from information
in software tickets.  They managed to successfully visualize the tracked features and illustrate 
their non apparent dependencies which can prove very useful in projects with a large number of
components.

The work of Just et. al \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
The authors ran a survey on 175 developers from Eclipse, Apache and Mozilla
Then, they applied a card sort in order to organize the comments into hierarchies to 
identify common patterns. Their findings can be summarized in the following top seven
suggestions:
  \begin{itemize}
    \item create differentiation between bug report difficulty levels between 
    novices and experiences reporters;
    \item encourage users to input as much information as possible;
    \item add ability to merge tickets when needed;
    \item recognise and reward valuable bug reporters;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item to be able to easily and expressively search through tickets.
  \end{itemize}

However, bug report assignment is not the only part of bug triaging that needs
investigation. Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
can predict the severity of a reported bug (i.e. assign story points to the 
ticket) automatically. The authors conducted their research on the Mozilla,
Eclipse and GNOME projects and divided their method into four steps:
  \begin{itemize}
    \item extract and organize bug reports;
    \item pre-process bug reports - tokenization, stop word removal and stemming;
    \item train the classifier on multiple datasets of bug reports - 70\% 
      training and 30\% evaluation;
    \item apply the trained classifier on the evaluation set.
  \end{itemize}
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
      a severe bug; however, there are other terms that can indicate the opposite,
      such as typos;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large dataset in order to predict correctly;
    \item depending on how well a software project is componentized, one can 
      use a predictor per component rather than an universal one.
  \end{itemize}

@@

Throughout the entire application, we tried to apply the UNIX philosophy of creating small applications that do one thing, but 
do it well. Therefore, we implemented clean and simple packages where we tried to use the standard library as much as possible
so that potential contributors coming to the project would find it easy to start working directly on the code. Also, we designed 
the tool with extensibility in mind, so that other database providers (e.g. CockroachDB) or issue tracking systems (e.g. Bugzilla) 
could be easily implemented - this was achieved using the elegant Go interfaces.

We split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
follow the flow shown in figure \ref{fig-eg} and complete the whole application cycle, in the end producing a database 
of analysed tickets, as well as plots and statistics for investigating correlations, saved on the filesystem.

In the following three subsections we describe how we designed and implemented the commands mentioned above.

@@

The decision of choosing Bolt in favor of well tested, more traditional databases such as Postgres or MySQL came naturally when 
we noticed that we did not need to query the database often, but rather get the whole array of tickets and manipulate them. Moreover, 
a MongoDB or Postgres DB would have required a running server. Even though the server could have been running on the local machine, 
Bolt instances are actually files with the extension \emph{db} saved on disk, thus it is trivial to create backups.

We have interacted with the Jira Server REST API which has very good documentation written by the Atlassian team. After getting
familiar with all the features the REST API offers, we have opted for getting paginated issues from the server, which means 
slicing the whole set of tickets into multiple smaller arrays to improve performance and reduce the load on the server. We also
specified to Jira exactly what set of issue fields to return and, eventually, while responses were retrieved from the instance,
we began storing them into our Bolt DB instance.

The way we chose to store them was to set the issue key (i.e. unique identifier that differentiates a ticket from all others across all 
projects inside a Jira instance) as the key of the pair and the value is the JSON representation of the ticket. This helped us reduce 
the size of the database once we reached hundreds of thousands of tickets.

@@

Another component of issues that we stored and proved to be crucial in our analysis is changelog histories together with their 
corresponding items. They represent the whole history of a ticket and can show status transitions, story points modifications, 
summary/description editing etc. What made them useful for our study was that we needed to see when tickets were marked closed and, 
as Jira does not provide this in a separate field, we looped through all changelog history items and saved when the transition to 
Closed or a similar status was made.

There are other fields that can be configured inside Jira, including custom fields, but we did not collect them as they would not 
have been helpful in conducting the analysis. However, in addition to the fields we saved, we also stored grammar correctness scores, 
sentiment scores, whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
Even though all of them, apart from grammar and sentiment scores, can be computed locally, we store them because of performance issues
due to the very large size of the database.

@@

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

All these numbers are also stored inside the database in a different bucket for easier access in the future. Moreover, the statistical 
tests we ran on the tickets are saved as well in the database.
